---
title: "C-Squared Quarto Theme"
subtitle: "Paper Wash and Night Bloom for analysis documents"
author: "Curtis Phills"
toc: true
title-block-banner: true
format:
  # Swap to csquared-paper-wash-html or csquared-night-bloom-html
  # to render a fixed palette without the Quarto theme toggle.
  csquared-html:
    embed-resources: true
---

## Overview

This document is a small rendering check for the C-Squared Quarto theme. It should feel clear, academic, artistic, and readable in toggle, fixed-light, and fixed-dark modes.

## Example Text

Bias is not inevitable. Reducing bias requires sustained effort, careful evidence, and attention to the social systems that shape perception.

> Intersectionality is not an add-on. It is part of social reality.

## Example Code

```{r}
#| echo: true
scores <- c(0.12, 0.18, 0.31, 0.27)
mean(scores)
```

## Example Tabset

::: {.panel-tabset}

### Load Pacman

Makes it easy to install and load multiple packages.

```{r}
#| echo: true
if (!require("pacman")) {
  install.packages("pacman", dependencies = TRUE)
  require(pacman)
}
```

### Import Data

Keeps import logic separate from cleaning logic.

```{r}
#| echo: true
data_path <- "data/saiat.csv"
```

:::

## Example Table

| Construct | Document role |
|---|---|
| Implicit bias | Core topic |
| Intersectionality | Organizing frame |
| Prejudice reduction | Applied payoff |

## Callout

::: {.callout-note}
The theme should add personality without making analysis documents feel decorative or hard to scan.
:::
